examine simulation results

### 2025-03-05 data-raw/examine_sim_results.Rmd
update site

```{r erodibility_2}
ggplot(wfs_meta, aes(ntr_pland, erodibility_mean)) + 
  geom_point()
```

>>>>

```{r erodibility_2}
library(plotly)
fig <- plot_ly(wfs_meta, x = ~erodibility_mean, y = ~erosivity_mean, z = ~delta_sed.margin, color = ~delta_sed.margin, text = ~hu)

fig

```{r sediment_change}
ggplot(wfs_meta, aes(sed_export_base, sed_export_max, color = delta_sed.margin)) + 
  geom_point() + geom_abline(intercept = 0, slope = 1) + scale_color_continuous(type="viridis")

```{r nutrient_change}
ggplot(wfs_meta, aes(n_export_base, n_export_max, color = delta_n_export.margin)) + 
  geom_point() + geom_abline(intercept = 0, slope = 1) + scale_color_continuous(type="viridis")

```{r pollinator_change}
ggplot(wfs_meta, aes(pollinators_base, pollinators_max, color = delta_pollinators.margin)) + 
  geom_point() + geom_abline(intercept = 0, slope = 1) + scale_color_continuous(type="viridis")

```{r qb_change}
ggplot(wfs_meta, aes(qb_base, qb_max, color = delta_qb.margin)) + 
  geom_point() + geom_abline(intercept = 0, slope = 1) + scale_color_continuous(type="viridis")
